\sys: Light-touch Data-Parallel Shell Processing

### 2020-05-09 pldi/draft.tex
Teensy corrections

To address this challenge, we develop \sys, a shell parallelizing POSIX shell scripts. % to their parallel equivalents.
% \sys offers both classes of users in the second group such much-needed automation.
\sys benefits both programmer groups mentioned earlier, with a particular emphasis on users.
Command developers are provided a set of abstractions, akin to lightweight type annotations, for expressing the parallelizability properties of their commands:
  rather than providing a command's full observable behavior, these annotations focus primarily on their interaction with state.
Shell users, on the other hand, are provided full automation:
  \sys extracts parallelism latent in their scripts by analyzing their parallelizability properties. % of their fragments.
% benefiting scripting experts and non-experts alike by offering automated POSIX-aware parallelization of shell-scripts as long as command developers
\sys's transformations are conservative, in that they do not attempt to parallelize fragments that lack sufficient information---\ie at worst, \sys will simply not improve performance, rather than risking breakage.

@@

\kk{Maybe use phoenix for that one? Since it has a MapReduce interface
  but it runs on multicore?}

>>>>

To address this challenge, we develop \sys, a shell parallelizing POSIX shell scripts. % to their parallel equivalents.
% \sys offers both classes of users in the second group such much-needed automation.
\sys benefits both programmer groups mentioned earlier, with a particular emphasis on users.
Command developers are provided a set of abstractions, akin to lightweight type annotations, for expressing the parallelizability properties of their commands:
  rather than providing a command's full observable behavior, these annotations focus primarily on their interaction with state.
Shell users, on the other hand, are provided full automation:
  \sys extracts parallelism latent in their scripts by analyzing their parallelizability properties. % of their fragments.
% benefiting scripting experts and non-experts alike by offering automated POSIX-aware parallelization of shell-scripts as long as command developers
\sys's transformations are conservative, in that they do not attempt to parallelize fragments that lack sufficient information---\ie at worst, \sys will choose to not improve performance rather than risking breakage.

@@

\kk{Maybe use phoenix for that one? Since it has a MapReduce interface
  but it runs on multicore?}
\nv{Phoenix (i) is shared-memory, and (ii) would require re-writing the entire program in C++, which defeats the purpose of comparing with an existing program. Phoenix might be OK for micro-benchmarks however.}
